$jk$-means tests

### 2016-09-06 Rmd/convergenceRates.Rmd
add empirical estimates for the convergence rate

```{r include=FALSE}
require('ggplot2')
require('reshape')
require('jkmeans')
```

@@

###2. Test jk-means/ j-sparse-GMM with different n

@@

```{r}
#code to run on an increasing series of n

if(FALSE)
{
  nSeries<- c(seq(20,100,by = 20),150,200,300,400,500)

@@

@@

>>>>

```{r include=FALSE}
require('ggplot2')
require('reshape')
require('jkmeans')

setwd("~/git/jkmeans/Rmd/")
```

@@

###2. Test jk-means/ j-sparse-GMM with different n's

@@

```{r}
#code to run on an increasing series of n
#ran on cluster

nSeries<- c(seq(20,500,by = 20))

if(FALSE)
{

@@

#Misclassification error
plot without & with pointwise 95% confidence band

@@

plot1<- data.frame( "n" = rep(nSeries, 4),
            "MC14Error"= c(result$MCEmean),
            "MC14ErrorL"= c(result$MCEq25),
            "MC14ErrorU"= c(result$MCEq975),
            "Model"= rep(c("K-Means","W-constraint-GMM (22-Means)","1-sparse-GMM","GMM"),each= length(nSeries))
            )

p<- ggplot(data=plot1, aes())
p<- p+  geom_line(aes(x= n, y=MC14Error, colour=Model)) 
pE<- p+  geom_line(aes(x= n, y=MC14ErrorL, colour=Model),linetype=2) 
pE<- pE+  geom_line(aes(x= n, y=MC14ErrorU, colour=Model),linetype=2)

# p+ geom_errorbar( aes(x=n,ymax = MC14ErrorU, ymin=MC14ErrorL, colour=Model),width=0.2)
p+ theme_bw()
pE + theme_bw()
```

#RMSE for the mean estimate
plot without & with pointwise 95% confidence band

plot1<- data.frame( "n" = rep(nSeries, 4),
            "RMSE"= c(result$RMSEmean),
            "RMSEL"= c(result$RMSEq25),
            "RMSEU"= c(result$RMSEq975),
            "Model"= rep(c("K-Means","W-constraint-GMM (22-Means)","1-sparse-GMM","GMM"),each= length(nSeries))
            )

p<- ggplot(data=plot1, aes())
p<- p+  geom_line(aes(x= n, y=RMSE, colour=Model))

pE<- p+  geom_line(aes(x= n, y=RMSEL, colour=Model),linetype=2) 
pE<- pE+  geom_line(aes(x= n, y=RMSEU, colour=Model),linetype=2)

p+ theme_bw()
pE + theme_bw()
```
